---
title: "Powerpoint template"
subtitle: "Presentation subtitle"
output-file: DHSC_powerpoint_example
author: "Author name"
date: today
format:
  DHSC-pptx
execute:
  echo: false
  warning: false
---

# Section header slide

## Guidance

**To do:**

-   Update the details at the top of the page for your presentation.

-   Create your powerpoint by choosing the types of slides you require and replacing the placeholder text with your contents.

-   To render the powerpoint, save this file and press render.

**Tips:**

-   Slides are defined with a level 2 heading (##).

-   To add bullet points, use a hyphen followed by 2 spaces then the text, and a blank line between each bullet point.

## Guidance (2)

-   Quarto has seven styles of slide layouts which it can use, as shown in this example. However, additional DHSC slide layouts can be manually added in PowerPoint after it has been rendered.

-   [Information about slide types](https://quarto.org/docs/presentations/powerpoint.html#slide-layouts).

-   Once rendered and in PowerPoint, you can make further changes if required.

## Guidance (3)

To add R code or an R output (see options on the [Quarto website](https://quarto.org/docs/reference/cells/cells-knitr.html#overview)).

To combine text with code outputs, the code chunk options need to be `results: asis` and the text needs to be within the `cat()` function.

```{r}
#| results: asis
cat(paste0("For example, there are ", nrow(mtcars), " cars in the mtcars dataset."))
```

## Title and Content slide

This is a Title and Content slide.

-   Bullet point 1

-   Bullet point 2

## 

::: notes
Speaker notes go here. This is a blank slide.
:::

## Two Content slide

::: columns
::: column
contents column 1...
:::

::: column
contents column 2...
:::
:::

## Comparison slide

::: columns
::: column
contents column 1...

```{r}
htmlTable::htmlTable(head(mtcars[1:2]))
```
:::

::: column
contents column 2...

```{r}
plot(head(mtcars[1:2]))
```
:::
:::

## Content with Caption

Text before the content.

```{r}
htmlTable::htmlTable(head(mtcars[1:2]))
```
