---
title: Untitled
output-file: DHSC_HTML_example
format:
  DHSC-html: default
execute:
  echo: false
  warning: false
---

This template is an example of how to write a report in the **DHSC** style.

You can edit this file and press the `Render` button to produce a HTML document.

When using the DHSC template, use one hash symbol for headings and two hash
symbols for subheadings and so on. Up to five levels of heading can be used (five
hash symbols).

You can learn more about controlling the appearance of HTML output on the [quarto website](https://quarto.org/docs/output-formats/html-basics.html).

# A heading

Some text here....

## A subheading

Text under a subheading...

# Further heading

More text here...

## A Subheading

Different text here...

### Third level subheading

#### Fourth level subheading

Some text here...

##### Fifth level subheading

## Another Subheading

More text here...

# Quarto HTML tips

Example of adding a table using the htmlTable package.

```{r Data table}

library(htmlTable)

htmlTable(head(iris, 10), rnames = FALSE)

```

Example of producing an interactive chart using the plotly package.

```{r Chart}

library(plotly)

fig <- plot_ly(
  data = iris,
  x = ~Sepal.Length,
  y = ~Petal.Length
) |> 
  config(displaylogo = FALSE,
         modeBarButtons = list(list("toImage")),
         toImageButtonOptions = list(format = "svg",
                                     filename = "Chart",
                                     width = 900,
                                     height = 640))

fig

```

Example of producing a tabset.

::: panel-tabset
# Tab 1

Text on tab 1.

# Tab 2

Text on tab 2.
:::
